This is the Regression portion of Group 1's class project for PUBPOL 542, Winter 2021.  


First we must read our RDS data file into Rstudio.  Note that we used "gzcon" to decompress the file. Without doing this, the file will not read properly and we will receive an error code.  
```{r}
df <- readRDS(gzcon(url(
  "https://github.com/PUBPOL-542-Group-1-Project/Merging-Dataframes/raw/main/datafiles/finaldata.RDS")))
summary(df)
```

Next, we have to call library DPLYR to use the %>% syntax , which is an important part of the renaming procedures that follow.  These next steps are changing the formatting for our column labels so they are more "R-Friendly". Once I've renamed these columns, I call the summary to double check that my changes went through. Also note that in Line 14, I've created a new fromPy, called fromPy3, that will reflect the changes.  This way I can preserve the formatting of the original.  
```{r}
#library(dplyr)
fromPy3 <- fromPy %>% rename(LowIncome = "Low-Income") %>% 
  rename(AllStudents = "All Students") %>% 
  rename(ELL = "English Language Learners") %>%
  rename(LowIncomeP = "Low-Income.p") %>%
  rename(MaleP = "Male.p") %>%
  rename(WhiteP = "White.p") %>%
  rename(ELLP = ELL.p)
summary(fromPy3)
```
Now onto the actual regression.  I set up three separate hypotheses, each involving a slightly different set of predictors.  I ran a Gaussian regression for all 3, with Low Income and Discipline in the first, then the additional White/Expenditure predictors in the second, then finally the same regression as step 2 with discipline removed.  Model 3 had a very similar rsquared to model 2, without the additional predictor, so I opted for model 3. Also note that low-income is only significant without white/expenditure included in the model.  Once these two factors are introduced, that predictor is no longer as relevant.    
```{r}
hypo1=formula(Graduate ~ LowIncome + DisciplineInt)
gauss1=glm(hypo1, 
           data=fromPy3,
           family="gaussian")
summary(gauss1)

hypo2=formula(Graduate ~ LowIncome + DisciplineInt + White + Expenditure)
gauss2=glm(hypo2,
           data=fromPy3,
           family="gaussian")
summary(gauss2)

hypo3=formula(Graduate ~ LowIncome + White + Expenditure)
gauss3=glm(hypo3,
           data=fromPy3,
           family="gaussian")
summary(gauss3)

fromPy4 <- fromPy3
fromPy4$DisciplineInt=NULL
fromPy4$SchoolName=NULL
corrmatrix1 <- cor(fromPy4)
corrmatrix1

anova(gauss1, gauss2, gauss3, test="Chisq")

#install.packages("rsq")
#library(rsq)
rsq(gauss1)
rsq(gauss2)
rsq(gauss3)
```
Now for my plots.  I created a dot and whisker plot for model 3, then plotted just the linear components (cplot) for "expenditure", "white", and "LowIncome".  I also did a 3D plot of my model with the "persp" function.  These are all useful visualizations for my model.  

```{r}
library(dotwhisker)
dwplot(gauss3,by_2sd = F)
library(margins)
cplot(gauss3, 'Expenditure')
cplot(gauss3, 'White')
cplot(gauss3, 'LowIncome')
persp(gauss3)

```

Now that I've plotted those, I will use the code provided by Professor M. to confirm the marginal effects of each of my predictors.  This is an extra step provided for a LOG regression, but it's nice to have confirmation nonetheless. Note that the marginal effects match the regression values given by Model 3 in prior steps.  
```{r}
(marginsINFO = margins(gauss3))
(marginsSUMM=summary(marginsINFO))

base= ggplot(marginsSUMM,
             aes(x=factor, y=AME))
base= base + geom_point()

plotMargins = base+ theme(axis.text.x = element_text(angle = 80,size = 6,hjust = 1))
plotMargins

plotMargins + geom_errorbar(aes(ymin=lower, 
                                ymax=upper))
```

THANKS FOR READING!

-Group 1 PUBPOL 542 WINTER 2021
(Micaela, Nick, Madelyn, and Wenzhen)

